Supplement to Manuscript for MADA Project

### 2023-04-24 products/supplement/Supplementary_Material.qmd
Additional Updates to MADA Project

---
title: "Supplement to Manuscript for MADA Project"
subtitle: "Supplement Materials"
author: Shiwani Sapkota
date: "`r Sys.Date()`"
format:
  pdf:
    toc: false
    number-sections: true
    highlight-style: github
bibliography: ../../dataanalysis_template_references.bib
csl: ../../vancouver.csl
---

```{r, echo=FALSE, message=FALSE}
# load a few R packages
library(knitr)
library(ipumsr)
library(readr)
library(skimr)
library(tidyverse)
library(dplyr)
library(survey)
library(naniar)
library(gmodels) #for ch-sq frequency table
library(vcd) # for three way frequency table
library(gtsummary)
library(openxlsx)
library(ggplot2)
library(ggthemes)
```

@@

# Saving the raw data file as .csv file and commenting out this code so it does not get created everytime we run this code chunk
# readr::write_csv(data, "mammogram_ses.csv")

@@

# Saving the raw data file as .rds file and commenting out this code so it does not get created everytime we run this code chunk
# saveRDS(data, "mammogram_ses1.rds")

# From here, you can follow general steps involved in data analysis and the
# respective codes are documented in the respected folders of this project:
# 1. Data cleaning
# 2. Exploratory Data analysis
# 3. Main statistical analysis
```

## Additional result

```{r}
#| label: Additional Table 1
#| tbl-cap: "Fit table using mammogram status as the outcome and age & hispanic_status as predictors."
#| echo: FALSE
additionaltable1 = readRDS(here("results", "statistical_analysis_result", "age_hispanic_model.rds"))
knitr::kable(additionaltable1)
```

```{r}
#| label: Additional Table 2
#| tbl-cap: "Fit table using mammogram status as the outcome and demographic characteristics variables as predictors."
#| echo: FALSE
additionaltable2 = readRDS(here("results", "statistical_analysis_result", "demographic_model.rds"))
knitr::kable(additionaltable2)
```

```{r}
#| label: Additional Table 3
#| tbl-cap: "Fit table using mammogram status as the outcome and the medical characteristics as the predictors."
#| echo: FALSE
additionaltable3 = readRDS(here("results", "statistical_analysis_result", "medical_model.rds"))
knitr::kable(additionaltable3)
```

```{r}
#| label: Additional Table 4
#| tbl-cap: "Fit table using mammogram status as the outcome and smoking & alcohol characteristics as the predictors."
#| echo: FALSE
additionaltable4 = readRDS(here("results", "statistical_analysis_result", "smoking_alcohol_model.rds"))
knitr::kable(additionaltable4)
```

```{r}
#| label: Additional Table 5
#| tbl-cap: "Model fitting table using mammogram status as the outcome and demographic characteristics as the predictors."
#| echo: FALSE
additionaltable5 = readRDS(here("results", "statistical_analysis_result", "1_model_fitting_result", "demographic_model.rds"))
knitr::kable(additionaltable5)
```

```{r}
#| label: Additional Table 6
#| tbl-cap: "Model fitting table using mammogram status as the outcome and medical characteristics as the predictors."
#| echo: FALSE
additionaltable6 = readRDS(here("results", "statistical_analysis_result", "1_model_fitting_result", "medical_model.rds"))
knitr::kable(additionaltable6)
```

```{r}
#| label: Additional Table 7
#| tbl-cap: "Model fitting table using mammogram status as the outcome and smoking and alcohol characteristics as the predictors."
#| echo: FALSE
additionaltable7 = readRDS(here("results", "statistical_analysis_result", "1_model_fitting_result", "smoking_alcohol_model.rds"))
knitr::kable(additionaltable7)
```

```{r}
#| label: Additional Table 8
#| tbl-cap: "Model fitting table using mammogram status as the outcome and year, age, and hispanic characteristics as the predictors."
#| echo: FALSE
additionaltable8 = readRDS(here("results", "statistical_analysis_result", "1_model_fitting_result", "year_age_hispanic_model.rds"))
knitr::kable(additionaltable8)
```

```{r}
#| label: Additional Table 9
#| tbl-cap: "Model performance comparison."
#| echo: FALSE
additionaltable9 = readRDS(here("results", "statistical_analysis_result", "1_model_fitting_result", "model_performance_comparison.rds"))
knitr::kable(additionaltable9)
```

```{r}
#| label: Additional Table 10
#| tbl-cap: "Model coefficients table using mammogram status as the outcome and other variables of interests as the predictors using model evaluation."
#| echo: FALSE
additionaltable10 = readRDS(here("results", "statistical_analysis_result", "2_model_evaluation_result", "logistic_full_model.rds"))
knitr::kable(additionaltable10)
```

```{r}
#| label: Additional Table 11
#| tbl-cap: "Model coefficients table using mammogram status as the outcome and hispanic status as the main predictor using model evaluation."
#| echo: FALSE
additionaltable11 = readRDS(here("results", "statistical_analysis_result", "3_machine_learning_result", "lasso_model_final_fit.rds"))
knitr::kable(additionaltable11)
```

```{r}
#| label: Additional Table 12
#| tbl-cap: "Lasso model final fit using machine learning approach."
#| echo: FALSE
additionaltable12 = readRDS(here("results", "statistical_analysis_result", "2_model_evaluation_result", "logistic_outcome_mainpredictor.rds"))
knitr::kable(additionaltable12)
```

```{r}
#| label: Additional Figure 1
#| fig-cap: "Lasso model."
#| echo: FALSE
knitr::include_graphics("/results/statistical_analysis_result/3_machine_learning_result/figure3_lasso_model.png")
```

# Discussion

[**To be added]

# References

[**To be added]

>>>>

---
title: "Supplement to Manuscript for MADA Project"
subtitle: "Supplement Materials"
author: Shiwani Sapkota
date: "`r Sys.Date()`"
format:
  pdf:
    toc: false
    number-sections: true
    highlight-style: github
---

```{r, echo=FALSE, message=FALSE}
# load a few R packages
library(knitr)
library(ipumsr)
library(readr)
library(skimr)
library(tidyverse)
library(dplyr)
library(survey)
library(naniar)
library(gmodels) #for chi-sq frequency table
library(vcd) # for three way frequency table
library(gtsummary)
library(openxlsx)
library(ggplot2)
library(ggthemes)
```

@@

# Saving the raw data file as .csv file and commenting out this code so it does not get created everytime we run this code chunk
# readr::write_csv(here("data", "raw_data", "mammogram_ses.csv")

@@

# Saving the raw data file as .rds file and commenting out this code so it does not get created everytime we run this code chunk
# saveRDS(here("data", "raw_data", "mammogram_ses1.rds")

# From here, you can follow general steps involved in data analysis and the
# respective codes are documented in the `code` folder with the given subfolders:
# 1. processing_cleaning_code folder
# 2. analysis_code folder
```

# List of Tables
# Additional results
# Exploratory Analysis

# Supplementary Table 1
```{r, message = FALSE}
#| echo: FALSE
# Loading the `demographic_table2.rds` table which was created during the data exploratory process
result_table1 <- readRDS(here("results", "exploratory_analysis_result", "demographic_table2.rds"))
result_table1
```

# Supplementary Table 2
```{r, message = FALSE}
#| echo: FALSE
# Loading the `demographic_table3.rds` table which was created during the data exploratory process
result_table2 <- readRDS(here("results", "exploratory_analysis_result", "demographic_table3.rds"))
result_table2
```

# Model Fitting
# Bivariate Logistic Regression

# Supplementary Table 3
```{r, message = FALSE}
#| echo: FALSE
# Loading the `bivariate_mammogram_year.rds` table which was created during the data fitting process
result_table3 <- readRDS(here("results", "statistical_analysis_result", "1_model_fitting_result", "bivariate_mammogram_year.rds"))
result_table3
```

# Supplementary Table 4
```{r, message = FALSE}
#| echo: FALSE
# Loading the `bivariate_mammogram_hispanic.rds` table which was created during the data fitting process
result_table4 <- readRDS(here("results", "statistical_analysis_result", "1_model_fitting_result", "bivariate_mammogram_hispanic.rds"))
result_table4
```

# Supplementary Table 5
```{r, message = FALSE}
#| echo: FALSE
# Loading the `bivariate_mammogram_age.rds` table which was created during the data fitting process
result_table5 <- readRDS(here("results", "statistical_analysis_result", "1_model_fitting_result", "bivariate_mammogram_age.rds"))
result_table5
```

# Supplementary Table 6
```{r, message = FALSE}
#| echo: FALSE
# Loading the `bivariate_mammogram_income.rds` table which was created during the data fitting process
result_table6 <- readRDS(here("results", "statistical_analysis_result", "1_model_fitting_result", "bivariate_mammogram_income.rds"))
result_table6
```

# Supplementary Table 7
```{r, message = FALSE}
#| echo: FALSE
# Loading the `bivariate_mammogram_education.rds` table which was created during the data fitting process
result_table7 <- readRDS(here("results", "statistical_analysis_result", "1_model_fitting_result", "bivariate_mammogram_education.rds"))
result_table7
```

# Supplementary Table 8
```{r, message = FALSE}
#| echo: FALSE
# Loading the `bivariate_mammogram_maritalstatus.rds` table which was created during the data fitting process
result_table8 <- readRDS(here("results", "statistical_analysis_result", "1_model_fitting_result", "bivariate_mammogram_maritalstatus.rds"))
result_table8
```

# Supplementary Table 9
```{r, message = FALSE}
#| echo: FALSE
# Loading the `bivariate_mammogram_regionresidence.rds` table which was created during the data fitting process
result_table9 <- readRDS(here("results", "statistical_analysis_result", "1_model_fitting_result", "bivariate_mammogram_regionresidence.rds"))
result_table9
```

# Supplementary Table 10
```{r, message = FALSE}
#| echo: FALSE
# Loading the `bivariate_mammogram_insurancestatus.rds` table which was created during the data fitting process
result_table10 <- readRDS(here("results", "statistical_analysis_result", "1_model_fitting_result", "bivariate_mammogram_insurancestatus.rds"))
result_table10
```

# Supplementary Table 11
```{r, message = FALSE}
#| echo: FALSE
# Loading the `bivariate_mammogram_healthstatus.rds` table which was created during the data fitting process
result_table11 <- readRDS(here("results", "statistical_analysis_result", "1_model_fitting_result", "bivariate_mammogram_healthstatus.rds"))
result_table11
```

# Supplementary Table 12
```{r, message = FALSE}
#| echo: FALSE
# Loading the `bivariate_mammogram_usualmedicalcarestatus.rds` table which was created during the data fitting process
result_table12 <- readRDS(here("results", "statistical_analysis_result", "1_model_fitting_result", "bivariate_mammogram_usualmedicalcarestatus.rds"))
result_table12
```

# Supplementary Table 13
```{r, message = FALSE}
#| echo: FALSE
# Loading the `bivariate_mammogram_smokingstatus.rds` table which was created during the data fitting process
result_table13 <- readRDS(here("results", "statistical_analysis_result", "1_model_fitting_result", "bivariate_mammogram_smokingstatus.rds"))
result_table13
```

# Supplementary Table 14
```{r, message = FALSE}
#| echo: FALSE
# Loading the `bivariate_mammogram_alcoholstatus.rds` table which was created during the data fitting process
result_table14 <- readRDS(here("results", "statistical_analysis_result", "1_model_fitting_result", "bivariate_mammogram_alcoholstatus.rds"))
result_table14
```

# Supplementary Table 15
```{r, message = FALSE}
#| echo: FALSE
# Loading the `bivariate_mammogram_diabetesstatus.rds` table which was created during the data fitting process
result_table15 <- readRDS(here("results", "statistical_analysis_result", "1_model_fitting_result", "bivariate_mammogram_diabetesstatus.rds"))
result_table15
```

# Supplementary Table 16
```{r, message = FALSE}
#| echo: FALSE
# Loading fit table using mammogram status as the outcome and year, age, & hispanic_status as predictors
result_table16 <- readRDS(here("results", "statistical_analysis_result", "1_model_fitting_result", "year_age_hispanic_model.rds"))
result_table16
```

# Supplementary Table 17
```{r, message = FALSE}
#| echo: FALSE
# Loading fit table using mammogram status as the outcome and demographic characteristics variables as predictors
result_table17 <- readRDS(here("results", "statistical_analysis_result", "1_model_fitting_result", "demographic_model.rds"))
result_table17
```

# Supplementary Table 18
```{r, message = FALSE}
#| echo: FALSE
# Loading fit table using mammogram status as the outcome and the medical characteristics as the predictors
result_table18 <- readRDS(here("results", "statistical_analysis_result", "1_model_fitting_result", "medical_model.rds"))
result_table18
```

# Supplementary Table 19
```{r, message = FALSE}
#| echo: FALSE
# Loading fit table using mammogram status as the outcome and smoking & alcohol characteristics as the predictors
result_table18 <- readRDS(here("results", "statistical_analysis_result", "1_model_fitting_result", "smoking_alcohol_model.rds"))
result_table18
```

# Model Evaluation

# Supplementary Table 20
```{r, message = FALSE}
#| echo: FALSE
 # Loading coefficients table using mammogram status as the outcome and other variables of interests as the predictors using model evaluation
result_table20 <- readRDS(here("results", "statistical_analysis_result", "2_model_evaluation_result", "logistic_full_model.rds"))
result_table20
```

# Supplementary Table 21
```{r, message = FALSE}
#| echo: FALSE
 # Loading coefficients table using mammogram status as the outcome and hispanic status as the main predictor using model evaluation
result_table21 <- readRDS(here("results", "statistical_analysis_result", "2_model_evaluation_result", "logistic_outcome_mainpredictor.rds"))
result_table21
```

# Machine Learning (Model Selection)

# Supplementary Table 22

```{r, message = FALSE}
#| echo: FALSE
 # Loading coefficients and penalty data during lasso model process
result_table22 <- readRDS(here("results", "statistical_analysis_result", "3_machine_learning_result", "lasso_model_final_fit.rds"))
result_table22
```

# List of Figures

# Machine Learning (Model Selection)

# Supplementary Figure 1
```{r}
#| label: Additional Figure 1
#| echo: FALSE

# Loading figure created using decision tree model for the final fit
suppl_fig1 <- knitr::include_graphics(here("results", "statistical_analysis_result", "3_machine_learning_result", "figure2_decision_tree_model.png"))
suppl_fig1
```
